\documentclass[12pt,a4paper]{moderncv}

% moderncv themes
\moderncvtheme[blue]{classic}                 % optional argument are 'blue' (default), 'orange', 'red', 'green', 'grey' and 'roman' (for roman fonts, instead of sans serif fonts)

% character encoding
\usepackage[utf8]{inputenc}                   % replace by the encoding you are using
\usepackage{hyperref}
% adjust the page margins
\usepackage[scale=0.8]{geometry}
%\setlength{\hintscolumnwidth}{3cm}						% if you want to change the width of the column with the dates
%\AtBeginDocument{\setlength{\maketitlenamewidth}{6cm}}  % only for the classic theme, if you want to change the width of your name placeholder (to leave more space for your address details
%\AtBeginDocument{\recomputelengths}                     % required when changes are made to page layout lengths

% personal data
\firstname{Mateusz}
\familyname{Haligowski}
\title{Curriculum Vitae}               % optional, remove the line if not wanted
\address{ul. Stawna 1C/45}{81-629 Gdynia}    % optional, remove the line if not wanted
\mobile{+48\,503\,702\,923}                    % optional, remove the line if not wanted
\email{mhaligowski@gmail.com}                      % optional, remove the line if not wanted
\extrainfo{\url{http://mhaligowski.github.io}}

% to show numerical labels in the biblaphy; only useful if you make citations in your resume
\makeatletter
\renewcommand*{\bibliographyitemlabel}{\@biblabel{\arabic{enumiv}}}
\makeatother

\begin{document}
\maketitle

\section{Experience}
\subsection{Professional}

\cventry{XI~2012 --}{Senior Java Developer (consultant)}{JIT Solutions sp. z o. o.}{}{}{
\textbf{since VII~2013 -- Young Digital Planet SA, Gdansk, Poland}\\
I took part in two projects in a strongly agile team. In the first project I was responsible for developing new functions in web application Java project which utilized Hibernate, Spring and GWT. Second project is a Rich Internet Application, written entirely in Java and GWT. Both of the applications are for educational sector.\\
\textbf{XI~2012 -- VI~2013 -- Nordea Bank Polska SA, Gdynia, Poland}\\
I worked in a major bank on a Polish market. I was responsible for implementng internal processes using tools such as Oracle Database and Oracle BPM.
}

\cventry{X~2011 -- XI~2012}{JEE Developer, Ruby on Rails Developer}{SpeedNet sp. z o. o.}{Gdynia, Poland}{}{I took part in a medium-sized project for the insurance industry. My tasks are both of the client layer (Google Web Toolkit, MVP4g, Google Gin) and the server layer (IBM WebSphere AS, JBoss AS, PostgreSQL, Oracle 10g, Google Guice, Hibernate, Drools). I was also responsible for migrating the application from JBoss AS/PostreSQL environment to IBM WebSphere AS/Oracle 10g.\\
Another major task was the analysis of usage of JBoss jBPM business process management framework. Since the analysis proved that it doesn't meet our requirements, I designed and implemented our own business process engine.\\
I also developed a worktime management plugin for a popular project management tool Redmine. The plugin was developed using Ruby on Rails framework.}

\cventry{I~2011 -- IX~2011}{JEE Developer}{Lufthansa Systems Poland/Hamburg S\"{u}d (consultant)}{Gdańsk,~Poland/Hamburg,~Germany}{}{As a JEE developer employed by Lufthansa Systems Poland I was doing my job in Hamburg, in one of the largest companies in the naval transportation industry. The project consisted of an application used in managament of the company’s fleet. I implemented the messaging system between own database and the external customers, using EJB and JMS in the OC4j application server with Oracle 11g database. I was also responsible for the deployment of Arquillian, a unit testing tool for Java Enterprise Edition.}

\cventry{II~2010 -- XII~2010}{Enterpreneurship}{Nostromo Labs}{Gdynia, Poland}{}{I started my own enterpreneurship, offering services in software development. I concentrated on Rich Internet Applications, using Python (Django), Ruby (Rails) and Java (GWT). I decided to shut it down after the offer from my next employer.}

\cventry{IX~2009 -- I~2010}{JEE Developer}{sprezentuj.pl}{Remote}{}{I worked remotely as a Java developer in an Internet startup company sprezentuj.pl, which was an on-line gift list. Main feature of the application was a windows-based user interface, created with the Google Web Toolkit library. I also learned to use Spring, Google Guice and Hibernate, used in lower layers.}

\cventry{VI~2008 -- IX~2009}{Consumer Credit Risk Management Specialist}{Meritum Bank ICB S.A.}{Gdańsk, Poland}{}{In my job in a bank I was responsible for creating and developing tools supporting the system of risk management of consumer credits, calculating the creditworthiness of customers and communication with financial istitutions. Among the tools I developed the major were credit scoring tool, made in Pyton and SQL, and reporting system, made in Java and SQL.}

\cventry{VIII~2007 -- X~2007}{Intern}{Thomson Reuters}{Gdynia, Poland}{}{As a student intern I was responsible for verifying macroeconomic data.}

\subsection{Training and certificates}
\cventry{XI~2013}{Functional Programming Principles in Scala}{}{Coursera.org}{}{}
\cventry{XI~2013}{M101J: MongoDB for Java Developers}{MongoDB University}{}{}{}
\cventry{XII~2010}{Adobe InDesign training}{Basic level}{Combidata}{Gdynia, Poland}{}{}
\cventry{IX~2010}{Adobe Illustrator training}{Basic level}{Combidata}{Gdynia, Poland}{}{}
\cventry{VII~2010}{Graphic design in advertisement and publication}{}{Combidata}{Gdynia, Poland}{}
\cventry{VII~2007}{Oracle PL/SQL with tuning for data analysts}{}{Altkom Akademia}{Gdynia, Poland}{}
\cventry{X~2006}{Sun Certified Java Programmer for Java 5}{}{}{}{}

\subsection{Given speeches}
\cventry{I~2013}{speaker}{tech.3camp.pl}{}{}{Big Data and Apache Hadoop(\href{http://www.3camp.pl/2013/01/film-przetwarzanie-big-data-w-chmurze-z-wykorzystaniem-apache-hadoop/}{video})}
\cventry{XI 2012}{workshop leader}{3hack.pl}{}{}{Apache Hadoop all-day workshop}
\cventry{X 2012}{speaker}{Trojmiasto Java User Group}{}{}{Apache Hadoop -- quick start (\url{http://mhaligowski.github.com/jug-hadoop-keynote})}
\cventry{X 2010}{speaker}{PyConPL'2010}{}{}{Real-time internet applications in Python}{}
\cventry{V~2008}{speaker}{,,Numerical methods in social science'' conference}{Quantitative Methods Science Club, Dept. of Management, University of Gdańsk}{}{Scientific Applications of Python}{}
\cventry{IV 2008}{speaker}{RuPy'2008}{}{}{Scientific Applications of Python}{}

\subsection{Other experience}
\cventry{X~2012 --}{contributor}{Django}{}{}{Contributing bug fixes and reviews for popular Python framework}
\cventry{V~2007 -- VIII~2007}{student participant}{Google Summer Of Code 2007}{Scribus Team}{}{I took part in Google Summer of Code programme, where I was to create an imposition plugin for Scribus desktop publishing suite. The plugin was made in C++, using Qt library.}{}

\section{Education}
\cventry{X~2008 -- IX~2010}{graduate studies}{Technical University of Gdańsk}{Departament of Electronics, Telecommunications and Computer Science}{Computer Science}{Master thesis: Task scheduling in uncertain conditions (in English).\tiny{\emph{in progress}}}  % arguments 3 to 6 can be left empty
\cventry{X~2008 -- IX~2010}{graduate studies}{University of Gdańsk}{Departament of Management}{Computer Science and Econometrics}{Master thesis: Analysis of effectiveness of pension funds in Poland in years 2002-2010 \tiny{\emph{interrupted}}}  % arguments 3 to 6 can be left empty
\cventry{X~2005 -- IX~2008}{undergraduate studies}{University of Gdańsk}{Departament of Management}{Computer Science and Econometrics}{Baccalaureate Thesis: Analysis of effectiveness of companies on many stock markets (in English)}  % arguments 3 to 6 can be left empty
\cventry{X~2005 -- VI~2006}{post-secondary college}{English Unlimited}{Translation study}{}{}{}
\cventry{IX~2002 -- V~2005}{secondary school}{III LO im. Marynarki Wojennej RP in Gdynia, Poland}{class with
an extended mathematics programme.}{}{}{}

\section{Foreign languages}
\cvlanguage{Polish}{native}{}
\cvlanguage{English}{fluent}{Certificate of Proficiency in English (C1), Test of English as a Foreign Language (99/120 pts)}
\cvlanguage{German}{good}{Zertifikat Deutsch (B1)}

\section{Skills}
\cvcomputer{Programming languages}{Java, Python, Javascript, Ruby, PL/SQL, C/C++}{Analytical tools}{R, MatLab, Statistica, SPSS, SQL}
\cvcomputer{Graphics tools}{Scribus, Gimp, \LaTeX}{Programming environments}{Eclipse, IntelliJ IDEA, Emacs, vim}
\cvcomputer{JEE containers}{IBM WebSphere AS, JBoss AS, Apache Tomcat, OC4J, Glassfish, OpenEJB}{Web frameworks}{Django, Ruby on Rails}

\section{Interests}
\cvline{Music}{\small I play bass guitar in a blues band Turbocola}
\cvline{Books}{\small Fantasy and science-fiction, but I read other genres as well}
\cvline{Electronics}{\small In my spare time I like to fiddle with electronics, mainly microprocessors and Arduino kit.}
\cvline{Science and new technologies}{\small I’m interested in all kinds of new technologies and I often read articles and books about that.}

\end{document}


%% end of file `template_en.tex'.
